Provenance analysis

### 2021-08-06 analysis/provenance2.Rmd

nrows <- min(14, nrow(provenance_sites))
r_vec("provenance name", nrows, if_else(provenance_sites$provenance == "", "NA", provenance_sites$provenance))
r_vec("nb provenance sites", nrows, provenance_sites$n)
r_vec("percent provenance sites", nrows, provenance_sites$pc)
r_vec("cumpercent provenance sites", nrows, provenance_sites$cpc)

>>>>

nrows <- min(14, nrow(provenance_sites))
r_vec("provenance name", nrows, case_when(provenance_sites$provenance == "" ~ "NA", 
                                          provenance_sites$provenance == "$" ~ "\\$",
                                          TRUE ~ provenance_sites$provenance))
r_vec("nb provenance sites", nrows, provenance_sites$n)
r_vec("percent provenance sites", nrows, provenance_sites$pc)
r_vec("cumpercent provenance sites", nrows, provenance_sites$cpc)
